Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
construct validity

%We must add construct validity.

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{|l|c|}
              \hline

              \textbf{Law}                              & \textbf{Applicability}    \\ \hline
              Continuing Change                         & True                      \\ \hline
              Increasing Complexity                     & Kinda                     \\ \hline
              Self Regulation                           & True                      \\ \hline
              Conservation of Organisational Stability  & False                     \\ \hline
              Conservation of Familiarity               & True                      \\ \hline
              Continuing Growth                         & True                      \\ \hline
              Declining Quality                         & Kinda                     \\ \hline
              Feedback System                           & True                      \\ \hline

>>>>

\noindent
\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the research questions around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}. Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis. This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase"). It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes. We consider this to be remaining threats to construct validity.

\smallskip \noindent
\textbf{Internal validity  }

\smallskip \noindent
\textbf{External validity  }

\smallskip \noindent
\textbf{Reliability  }

1
Theories not applying
Only analysing changes between two version
Not investigating the implementation of the code (i.e. only headers were analysed)

2
Counteracted: 
Triangulation by checking both code, documentation and interviewing.

Remaining: 
Only interviewing architects. Maybe business ppl need to be invited to find intents.
Not interviewing partners

3
The results should be generalisable to a large extent to any API designers
Should be especially useful for platform/embedded APIs

4
This threat has bene counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
The analysis of the data is based around existing theories which should also help reproducability.
The inteview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducability.

@@

\begin{table}
       \centering
       \begin{tabular}[ht]{l|c}
              \toprule

              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
              Continuing Change                         & True                      \\ \hline
              Increasing Complexity                     & Kinda                     \\ \hline
              Self Regulation                           & True                      \\ \hline
              Conservation of Organisational Stability  & False                     \\ \hline
              Conservation of Familiarity               & True                      \\ \hline
              Continuing Growth                         & True                      \\ \hline
              Declining Quality                         & Kinda                     \\ \hline
              Feedback System                           & True                      \\

              \bottomrule
